%-------------------------------------------------------------------------------
% CONFIGURATION
%-------------------------------------------------------------------------------

\documentclass[11pt, a4paper]{russell}

\usepackage{xcolor}

\geometry{left=1.4cm, top=.8cm, right=1.4cm, bottom=1.8cm, footskip=.5cm}

\fontdir[fonts/]

\colorlet{russell}{russell-black}

\setbool{acvSectionColorHighlight}{true}

\renewcommand{\acvHeaderSocialSep}{\quad\textbar\quad}


%-------------------------------------------------------------------------------
% PERSONAL INFORMATION
%-------------------------------------------------------------------------------

\name{Victor Augusto}{Tramontina}

\position{Computer Engineering -- \textbf{Full Stack Developer}}

\mobile{+55 (54) 9 9937-7877}

\email{victor.tramontina@universo.univates.br}

\github{https://github.com/VicTramontina}

% \linkedin{linkedin.com/in/victor-augusto-tramontina-ba3b26299}


%-------------------------------------------------------------------------------
\begin{document}

    \makecvheader

    \makecvfooter{}{Victor Augusto Tramontina}{\thepage}


%-------------------------------------------------------------------------------
% SUMMARY
%-------------------------------------------------------------------------------

    \cvsection{About Me}

    \begin{cvparagraph}
        \textbf{Motivated and collaborative full stack developer} with strong problem-solving skills and a solid background in \textbf{backend (Vanilla PHP, SQL)} and \textbf{modern frontend (ReactJS, TailwindCSS, Styled Components)}. Experienced in maintaining legacy systems, refactoring architectures, and integrating \textbf{cloud services (AWS)} and third-party APIs (OAuth2). Frequently leverages \textbf{AI tools and assistants} to support coding, debugging, and technical decision-making. Enthusiastic about learning and sharing knowledge, with an active role in \textbf{team discussions and technology decisions}.
    \end{cvparagraph}


%-------------------------------------------------------------------------------
% SKILLS
%-------------------------------------------------------------------------------

    \cvsection{Skills}

    \begin{cvskills}
        \cvskill{Frontend}{ReactJS, TailwindCSS, Styled Components, React Hook Form, Zod}
        \cvskill{Backend}{Vanilla PHP, Node, SQL, REST APIs, OAuth2}
        \cvskill{DevOps \& Tools}{Docker, Git, AWS (EC2, S3, Lambda, Cognito, Amplify), Linux, Crontabs}
        \cvskill{Mobile}{React Native, Java, Android Studio, SQLite}
        \cvskill{Integration}{Payment gateways, ERP platforms, Notifications and e-mail systems}
    \end{cvskills}


%-------------------------------------------------------------------------------
% EXPERIENCE
%-------------------------------------------------------------------------------

    \cvsection{Professional Experience}

    \begin{cventries}
        \cventry
        {\textbf{Full Stack Developer}}
        {Macro Publicidade -- Conecta Venda System}
        {Brazil}
        {2022 -- Present}
        {
            \begin{cvitems}
                \item {Worked in a \textbf{small agile team} (5 members) using \textbf{Scrum methodology}.}
                \item {Maintained \textbf{legacy PHP systems} and refactored old AngularJS frontends into \textbf{ReactJS}.}
                \item {Helped architect and implement \textbf{system-wide improvements} in frontend and database models.}
                \item {Developed \textbf{reusable frontend components} and backend utilities to streamline workflows.}
                \item {Participated in \textbf{technical decision-making}, mentoring junior teammates, and improving team practices.}
                \item {Integrated external services using \textbf{OAuth2}, including payment gateways and ERP systems.}
                \item {Handled \textbf{deployments and environment management} using Docker and AWS.}
                \item {Contributed to the digital transformation of the company's systems, improving maintainability and scalability.}
            \end{cvitems}
        }
    \end{cventries}


%-------------------------------------------------------------------------------
% PROJECTS
%-------------------------------------------------------------------------------

    \cvsection{Personal Projects}

    \begin{cventries}
        \cventry
        {Guaporé - RS}
        {Android Ticketing System}
        {2023}
        {}
        {
            \begin{cvitems}
                \item {Developed a \textbf{complete Android app} for ticket printing and bar sales management.}
                \item {Implemented product registration, order creation and report exports.}
                \item {System is used by \textbf{over 8 companies} in the city.}
                \item {Technologies used: \textbf{Java, Android Studio, SQLite, Epson SDK}.}
            \end{cvitems}
        }
    \end{cventries}


%-------------------------------------------------------------------------------
% EDUCATION
%-------------------------------------------------------------------------------

    \cvsection{Education}

    \begin{cventries}
        \cventry
        {Computer Engineering}
        {Univates}
        {Brazil}
        {2022 -- Present, \textbf{7th Semester}}
        {}
    \end{cventries}


%-------------------------------------------------------------------------------
% LANGUAGES
%-------------------------------------------------------------------------------

    \cvsection{Languages}

    \begin{cvskills}
        \cvskill{Portuguese}{\textbf{Native}}
        \cvskill{English}{\textbf{Advanced}}
    \end{cvskills}


%-------------------------------------------------------------------------------
\end{document}
