%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Software Engineer} % Job title
    {Dell Technologies} % Organization
    {Eldorado do Sul/Brazil} % Location
    {Feb 2025 - Present} % Date(s)
    {
      \begin{cvitems} % Description
        \item {Develop and optimize \textbf{high-throughput Spring Boot Reactive APIs} handling \textbf{200M+ requests/day} with rigorous unit and integration testing, focusing on latency reduction and resilience.}
        \item {Architected microservices to improve query efficiency, reducing 95th-percentile latency by \textbf{40\%} via caching (\textbf{Redis}) and async processing.}
        \item {Migrated legacy services to \textbf{Kubernetes (KOB)}, improving scalability and resource utilization.}
        \item {\textbf{Tech:} Java/Spring Boot Reactive, MongoDB, Redis, Kubernetes, Dynatrace, Kafka, OracleSQL.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Software Engineer Junior} % Job title
    {} % Organization
    {} % Location
    {Aug 2023 - Jan 2025} % Date(s)
    {
      \begin{cvitems} % Description
        \item {Built and maintained \textbf{microservices} (Spring Boot) in a distributed architecture, using \textbf{Kafka/RabbitMQ} for event-driven workflows.}
        \item {Automated CI/CD pipelines (\textbf{GitLab}) and infrastructure provisioning, reducing deployment time.}
        \item {Led vulnerability fixes and monitoring integration with \textbf{Dynatrace}, improving system reliability.}
        \item {\textbf{Tech:} Java/Spring Boot, Python, OracleSQL, MongoDB, Kafka, Kubernetes, GitLab CI/CD.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Intern} % Job title
    {} % Organization
    {} % Location
    {May 2022 - Jul 2023} % Date(s)
    {
      \begin{cvitems} % Description
        \item {Developed RESTful APIs and microservices in \textbf{Spring Boot}, integrating with \textbf{Redis} (caching) and \textbf{OracleSQL}.}
        \item {Created \textbf{bash scripts} to automate deployments and diagnostics, saving \textbf{5+ hours/week} in manual work.}
        \item {\textbf{Tech:} Java/Spring Boot, PCF, HashiCorp Vault, GitLab CI/CD, RabbitMQ, Kafka}
      \end{cvitems}
    }
\end{cventries}